Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-01 Paper/main.tex
Adding more to paper
Add governing equations section
Added Nate's section

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{longtable,tabularx}
\usepackage{fixme}
\setlength\LTleft{0pt}

@@

\fxnote{Mention study by \cite{wurps2020grid}.  Nate's piece goes here.}

>>>>

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[version=4]{mhchem}
\usepackage{siunitx}
\usepackage{longtable,tabularx}
\usepackage{fixme}
\setlength\LTleft{0pt}
\hypersetup{
  colorlinks=true
}

@@

\subsection{Prevous work}

\fxnote{Nate's piece goes here.  Edit and merge with above.}

Stably stratified boundary layers, or SBL, commonly occur on clear nights over land, in polar regions, and over cold oceans. Given that wind turbines are likely to experience the SBL as part of the diurnal cycle, or as part of there general locale, it is of utmost import to model such conditions correctly. Large eddy simulation, or LES, of the SBL presents certain challenges compared to neutral and convective stability states, stemming primarily from small dominant eddy length scales and low turbulence intensity. These challenges require higher resolution grids and/or advanced subgrid scale (SGS) models. As such, LES research of the SBL has been slower to evolve than the other stability states.

The first successful LES of the SBL was published by Mason and Derbyshire in 1990 \cite{Mason1990}. They used a strategy of simulating a near steady-state neutral stability turbulent simulation, then added a cooling-surface boundary to develop the stable ABL. They recorded a need for implausibly strong initial perturbations to sustain turbulence using the Smagorinsky SGS model. Brown et al.\ \cite{Brown1994} worked with Mason and Derbyshire to add stochastic backscatter to the SGS model, resulting in better agreement with surface layer observations. Andren, \cite{Andren1995}, simulated two SBL types, one with a neutral layer aloft, and one capped by an inversion, comparing two SGS models. He found significant improvements with the Sullivan SGS model, on par with the earlier backscatter model. In 1995, Derbyshire flew two measurement balloons, one in a heterogeneous location, another in a more idealized location, with the hope that the measurements would be useful for comparison to LES. He found significant variation in the critical Richardson number, and the temperature structure led him to state that complete comparison with LES had little point. Kemp and Thompson \cite{Kemp1996} used the same model as \cite{Brown1994} to study particle dispersion, but the LES code did not replicate an expected plume growth. Derbyshire wrote a review of SBL modeling along with future projections in 1999 \cite{Derbyshire1999}, with discussion of the importance of local Richardson number, a general statement that LES is a good supplement to SBL observations, and identification of a need to go to higher resolutions in SBL research.

In 2000, Kosovic and Curry \cite{Kosovic2000} used an LES simulation with a nonlinear SGS model containing backscatter to favorably compare to the BASE measurements, showing that the SBL could reach a quasi steady-state. They also showed good agreement with the Nieustadt analytical model. In the same year, Saiki et al. \cite{Saiki2000} simulated an SBL with a strong capping inversion at z=500m, producing reasonable surface layer profiles and identifying a need for SBL specific SGS models. Beare and MacVean \cite{Beare2004} presented the first grid-focused work on LES of the SBL, using grids with deltas between 2m and 12.5m, finding significant variation between grid sizes. The inclusion of a backscatter model resulted in significant variation at a 6.25m resolution, but very little at a 2m resolution. Basu et al. \cite{Basu2005} published a set of turbulence statistics, measurements, and supporting LES simulations in support of the viability of Nieustadt's local scaling hypothesis under very stable conditions. Jimenez and Cuxart \cite{Jimenez2005} set out to quantify the range for which standard SGS models, using the Kolmogorov theory for dissipation, were valid for increasingly stable flows. They found the model to perform adequately for weakly stable, and some moderately stable flow regimes.

An inter-comparison of LES simulations of the SBL was organized in 2006, the results of which are published in Beare et al.\ \cite{Beare2006}. Collectively, this is knows as the GABLS initiative, and involved simulating a moderately stable flow taken from Kosovic and Curry \cite{Kosovic2000}. Eleven codes were compared in all, and in general, grid deltas of less than 12.5m were found successful at maintaining resolved turbulence, and at grid deltas less than 3.125m showed little statistical change. The comparison also identified that Smagorinsky constants less than 0.2 were desirable, and that results became independent of SGS at 1m resolution. In the same year, Kumar et al. \cite{Kumar2006} successfully simulated an entire diurnal cycle with LES using a Lagrangian dynamic scale dependent SGS model. Stoll and Porte-Agel \cite{Stoll2007} compared three grid refinements and three scale dependent dynamic SGS models, showing that the Lagrangian and locally averaged models reproduced important flow features. The work of van Dop and Axelsen \cite{vanDop2007} provided even more evidence in support Nieuwstadt's local scaling hypothesis for SBLs. Chow and Zhou \cite{Chow2011} showed evidence that the Smagorinsky model is simply too dissipative for use in strongly stable flows.

The scale dependent Lagrangian SGS model has been used by several researchers since 2011, including Lu and Porte-Agel \cite{Lu2011}, Huang and Bou-Zeid \cite{Huang2013}, Park et al.\ \cite{Park2014}, and Abkar and Porte-Agel \cite{Abkar2015}. Recent work in LES of the SBL includes Matheou \cite{Matheou2016} who explored a large parameter space using the Smagorinsky-Lilly SGS closure. Several researchers have applied SBL simulation in the wind energy space \cite{Aitken2014, Abkar2015, Ghaisas2017}. This year, Wurps et al. \cite{Wurps2020} provided a rigorous grid resolution study for the SBL, looking at mean flow, turbulence variables, and two-point correlations, using a dynamic SGS model that allows backscatter. They found grid requirements to be 2.5m, 10m, and 20m for stable, neutral, and convective boundary layers respectively. They also found Pope's resolution requirement ratio of resolved energy to total energy of $\gamma < 0.8$ to be too lax in many cases. They advocate looking at two point correlations in order to quantify flow structure size, which in turn provides a basis for choice of grid resolution.

\subsection{Study objective and outline}

The current paper is organized as follows.
